Alex's Notes and Text Fragments for the JOSS Manuscript

### 2021-05-02 paper/paper.Rmd
restructure partitioning methods section

```{r create task, cache=TRUE}
library(mlr3)
library(mlr3spatiotempcv)

@@

@@

\begin{table}[h]
  \centering
  \caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column). }
  \begingroup
  \begin{adjustbox}{angle=270}
    \begin{tabular}{lllll}
      \\
      Type                            & Name                        & R Package(s)     & mlr3 Notation  & Literature \\
      \toprule
      \multirow{3}{*}{Spatial}        & Spatial Buffering           & \pkg{blockCV}, \pkg{sperrorest}    & "spcv\_buffer", "spcv\_disc()", "spcv\_loo()" & Lit1       \\
                                      & Spatial Blocking            & \pkg{blockCV}, \pkg{sperrorest}  & "spcv\_block",
                                      "spcv\_tiles()"  & Lit1       \\
                                      & Spatial Clustering          & \pkg{sperrorest} & "spcv\_coords" & Lit1       \\
       & Leave-Location-Out & \pkg{CAST}, \pkg{sperrorest}       & "sptcv\_cstf('space\_var')", "spcv\_factor"  & Lit1       \\
      \midrule
      \multirow{2}{*}{Spatiotemporal} & Leave-Location-and-Time-Out & \pkg{CAST}       & "sptcv\_cstf"  & Lit1       \\
                                      & Spatiotemporal Clustering   & \pkg{skmeans}    & "sptcv\_cluto" & Lit1       \\
      \midrule
      Feature space                   & Environmental Blocking      & \pkg{blockCV}    & "spcv\_env"    & Lit1       \\
    \end{tabular}
  \end{adjustbox}
  \endgroup\label{tab:sptcv-methods}
\end{table}

@@

## Spatial buffering

@@

## Spatial blocking

@@

### Option: selection = "random"

@@

### Option: selection = "systematic"

@@

### Option: selection = "checkerboard"

@@

### Rectangular blocks

@@

## Environmental Blocking

```{r env-1, fig.cap="Environmental blocking using a single predictor.", cache=TRUE, out.width="50%", fig.pos="ht"}
resampling_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

```{r env-2, fig.cap="Environmental blocking using multiple predictors.", cache=TRUE, out.width="50%", fig.pos="ht"}
resampling_env_multi = rsmp("spcv_env",
  features = c("distdeforest", "slope"), folds = 5)

## Spatial CV

@@

## CreateSpacetimeFolds (Cstf)

Leave-Location-and-Time-Out from packge \pkg{CAST} is a spatiotemporal resampling method [@meyer2018a].
It requires both a spatial and a temporal variable which are used to to separate observations in a multi-dimensional space.
It comes with satellite methods named "Leave-time-out" (LTO) and "Leave-location-out" (LLO) which only operatre in a two-dimensional space.

@@

### Leave-Time-Out (LTO)

@@

### Leave-Location-Out (LLO)

@@

### Leave-Location-and-Time-Out (LLTO)

@@

## Spatiotemporal Clustering (Cluto)

>>>>

```{r create task, cache=F}
library(mlr3)
library(mlr3spatiotempcv)

@@

## Spatial

### Buffering

@@

\begin{table}[h]
  \centering
  \caption[t]{Spatiotemporal resampling methods, ordered alphabetically by class name (Notation column). }
  \begingroup
  <!-- \begin{adjustbox}{angle=270} -->
    \begin{tabular}{lllll}
      \\
      Type                            & Name                        & R Package(s)     & mlr3 Notation  & Literature \\
      \toprule
      \multirow{3}{*}{Spatial}        & Spatial Buffering           & \pkg{blockCV}, \pkg{sperrorest}    & "spcv\_buffer", "spcv\_disc()", "spcv\_loo()" & Lit1       \\
                                      & Spatial Blocking            & \pkg{blockCV}, \pkg{sperrorest}  & "spcv\_block",
                                      "spcv\_tiles()"  & Lit1       \\
                                      & Spatial Clustering          & \pkg{sperrorest} & "spcv\_coords" & Lit1       \\
       & Leave-Location-Out & \pkg{CAST}, \pkg{sperrorest}       & "sptcv\_cstf('space\_var')", "spcv\_factor"  & Lit1       \\
      \midrule
      \multirow{2}{*}{Spatiotemporal} & Leave-Location-and-Time-Out & \pkg{CAST}       & "sptcv\_cstf"  & Lit1       \\
                                      & Spatiotemporal Clustering   & \pkg{skmeans}    & "sptcv\_cluto" & Lit1       \\
      \midrule
      Feature space                   & Environmental Blocking      & \pkg{blockCV}    & "spcv\_env"    & Lit1       \\
    \end{tabular}
  <!-- \end{adjustbox} -->
  \endgroup\label{tab:sptcv-methods}
\end{table}

@@

#### Spatial buffering (blockCV)

@@

#### Spatial disc (sperrorest)

### Blocking

#### Spatial blocking (blockCV)

@@

##### Option: selection = "random"

@@

##### Option: selection = "systematic"

@@

##### Option: selection = "checkerboard"

@@

##### Rectangular blocks

@@

#### Spatial tiling (sperrorest)

### Spatial Clustering (sperrorest)

#### Coordinate-based clustering

@@

### Feature space clustering (blockCV)

```{r env-1, fig.cap="Environmental blocking using a single predictor.", cache=F, out.width="50%", fig.pos="ht"}
resampling_env = rsmp("spcv_env",
  features = "distdeforest", folds = 5)

```{r env-2, fig.cap="Environmental blocking using multiple predictors.", cache=T, out.width="50%", fig.pos="ht"}
resampling_env_multi = rsmp("spcv_env",
  features = c("distdeforest", "slope"), folds = 5)

## Spatiotemporal

### Factor-based grouping

#### Predefined grouping

FIXME

#### Leave-Location-And-Time-Out (CAST)

Leave-Location-and-Time-Out (LLTO) from packge \pkg{CAST} is a spatiotemporal resampling method [@meyer2018a].
It requires both a spatial and a temporal variable which are used to to separate observations in a multi-dimensional space.
It comes with satellite methods named "Leave-time-out" (LTO) and "Leave-location-out" (LLO) which only operate in a two-dimensional space.

@@

##### Leave-Time-Out (LTO)

@@

##### Leave-Location-Out (LLO)

@@

##### Leave-Location-and-Time-Out (LLTO)

@@

### Spatiotemporal Clustering (skmeans)
